Wide Post-Mass Transfer White-Dwarf Binaries

### 2024-07-30 summaries/paper-draft-plain.tex
add population statistics to high mass MT

We ran COSMIC binary evolution simulation of a $7\Msun + 1\Msun$ system and investigate how the final separation $a_f$ depends on the initial separation $a_i$ and the CE parameter $\lambda$. The initial separation is a linear grid in range $2 \sim 8 \au$ with $400$ points. The CE flag \verb|lambdaf| is a linear grid in range $0 \sim -100$ with $2000$ steps, which corresponds to $0 \sim 100$ for CE parameter $\lambda$. Also, we ran these parameters with four different CE efficiencies — $\alphace = 1$, $\alphace = 0.9$, $\alphace = 0.6$, and $\alphace = 0.3$, the same as recorded in \cite{yamaguchi_hi}. In total, for each of the $4$ different CE efficiency $\alphace$, we ran a grid of $80000$ binary star systems with different initial separation $a_i$ and CE parameter $\lambda$.

@@

A typical change of \verb|evol_type| through the evolution is $\boxed{\text{\textbf{*-3-7-8-4-*-3-7-8-4-*}}}$ (refer to Section \ref{sec:intro} for correspondence between \verb|evol_type| and evolutionary changes), where WD+MS is reached during the second mass transfer process. Another possible change of \verb|evol_type| through the volution is $\boxed{\text{\textbf{*-3-7-8-7-8-4-*}}}$. It is worth noting that most of these systems experience two mass transfer phases in COSMIC before reaching WD+MS. That is, during the evolution process, two CE processes take place, between which there is a period of time. Statistically, we found that \textbf{(***TO-DO***)} fraction of all our $320000$ simulated binaries experience two CE processes before reaching WD+MS. To explain this qualitatively, we notice that when the primary loses too much mass during the first CE, the CE process ends, as the radius of the primary becomes smaller than the Roche lobe. After the primary fills its Roche lobe and has a large enough envelope again, the CE process resumes and causes two CE processes in total.

@@

We take the same approach as high mass systems to investigate the effective value of $\lambda$ in COSMIC that matches with the results in MESA. The initial separation is a linear grid in range $0.5 \sim 6 \au$ with $400$ points. The CE flag \verb|lambdaf| is a linear grid in range $0 \sim -100$ with $2000$ steps, which corresponds to $0 \sim 100$ for CE parameter $\lambda$. Also, we ran these parameters with four different CE efficiencies — $\alphace = 1$, $\alphace = 0.9$, $\alphace = 0.6$, and $\alphace = 0.3$, the same as recorded in \cite{yamaguchi_lo}. In total, for each of the $4$ different CE efficiency $\alphace$, we ran a grid of $80000$ binary star systems with different initial separation $a_i$ and CE parameter $\lambda$.

@@

Typical \textbf{pre-spike} and \textbf{spike} systems both follows the evolution path $\boxed{\text{\textbf{*-3-*-5-7-8-4-*-3-*-4-*}}}$ before reacing WD+MS. Note that the binaries come into contact (\verb|evol_type = 5|), which follows by a common enevelope phase. After inspecting the evolutionary process more closely, we found that the second stable mass transfer tends to widens the orbit significantly. \textbf{(***TO-DO***)}

>>>>

We ran COSMIC binary evolution simulation of a $7\Msun + 1\Msun$ system and investigate how the final separation $a_f$ depends on the initial separation $a_i$ and the CE parameter $\lambda$. The initial separation is a linear grid in range $2 \sim 8 \au$ with $400$ points. The CE flag \verb|lambdaf| is a linear grid in range $0 \sim -100$ with $2000$ steps, which corresponds to $0 \sim 100$ for CE parameter $\lambda$. Also, we ran these parameters with four different CE efficiencies — $\alphace = 1$, $\alphace = 0.9$, $\alphace = 0.6$, and $\alphace = 0.3$, the same as recorded in \cite{yamaguchi_hi}. In total, for each of the $4$ different CE efficiency $\alphace$, we ran a grid of $800000$ binary star systems with different initial separation $a_i$ and CE parameter $\lambda$.

@@

Among the 3200000 binary star systems we simulated, a typical change of \verb|evol_type| through the evolution is $\boxed{\text{\textbf{3-7-8-4-3-7-8-4}}}$ (refer to Section \ref{sec:intro} for correspondence between \verb|evol_type| and evolutionary changes, kstar changes and other evolutionary changes before and after the mass transfer are omitted), where WD+MS is reached during the second mass transfer process. Another possible change of \verb|evol_type| through the volution is $\boxed{\text{\textbf{3-7-8-7-8-4}}}$. It is worth noting that most of these systems experience two mass transfer phases in COSMIC before reaching WD+MS. That is, during the evolution process, two CE processes take place, between which there is a period of time. Statistically, 3146556 of the 3200000 binaries (98\%) we simulated reach WD+MS in their evolutionary process. In these 3146556 binaries, 2660287 of them went through two CE processes before reaching WD+MS (85\%). To explain this qualitatively, we notice that when the primary loses too much mass during the first CE, the CE process ends, as the radius of the primary becomes smaller than the Roche lobe. After the primary fills its Roche lobe and has a large enough envelope again, the CE process resumes and causes two CE processes in total. On the contrary, for the rest of the population that reached WD+MS with only one CE, the mass loss of the primary is not enough for the first CE to stop, and the evolution reaches WD+MS directly.

@@

We take the same approach as high mass systems to investigate the effective value of $\lambda$ in COSMIC that matches with the results in MESA. The initial separation is a linear grid in range $0.5 \sim 6 \au$ with $400$ points. The CE flag \verb|lambdaf| is a linear grid in range $0 \sim -100$ with $2000$ steps, which corresponds to $0 \sim 100$ for CE parameter $\lambda$. Also, we ran these parameters with four different CE efficiencies — $\alphace = 1$, $\alphace = 0.9$, $\alphace = 0.6$, and $\alphace = 0.3$, the same as recorded in \cite{yamaguchi_lo}. In total, for each of the $4$ different CE efficiency $\alphace$, we ran a grid of $800000$ binary star systems with different initial separation $a_i$ and CE parameter $\lambda$.

@@

Typical \textbf{pre-spike} and \textbf{spike} systems both follows the evolution path $\boxed{\text{\textbf{3-5-7-8-4-3-4}}}$ before reacing WD+MS. Note that the binaries come into contact (\verb|evol_type = 5|), which follows by a common enevelope phase. After inspecting the evolutionary process more closely, we found that the second stable mass transfer tends to widens the orbit significantly. \textbf{(***TO-DO***)}
